Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-03-06 paper/gloaguenAppliedNMF.tex
add mTIR paragraph

With this built-up database, the \textit{SimScene} software and the annotations of the recordings, 74 simulated sound scenes are generated, which have the same temporal structure than the recordings. The \textit{ebr} parameter is adjusted manually on each sound scene to be faithful compared to the recorded scenes. To validate its realism, the corpus of transcribed urban sound scenes is submitted to a perceptual test.

>>>>

\begin{table}[t]
\centering
\caption{$mTIR$ for each sound environment}
\begin{tabular}{lc}
 & $mTIR$ (dB)\\ \hline
 park & -9.10 ($\pm$ 7.35) \\
 quiet street & 0.88 ($\pm$ 5.92) \\
 noisy street & 6.96 ($\pm$ 5.16) \\
 very noisy street & 15.75 ($\pm$ 9.78) \\ \hline
\end{tabular}
\label{tab:mTIR}
\end{table}

With this built-up database, the \textit{SimScene} software and the annotations of the recordings, 74 simulated sound scenes are generated, which have the same temporal structure than the recordings. The \textit{ebr} parameter is adjusted manually on each sound scene to be faithful compared to the recorded scenes. To validate this adjustment, the mean \textit{Traffic Interfering Ratio} is calculated and summarized on Table \ref{tab:mTIR}. It expresses, on all the scenes of an sound environment, the mean difference between the equivalent traffic sound levels of each scene, $L_{p,traffic}$, with the sound level of the \textit{interfering} sound class, $L_{p, interfering}$, which gathered all the other sound sources not related to the traffic, see Eq \ref{eq:mTIR}. It quantifies the predominance of the traffic component on the 4 sound environments.

\begin{equation}\label{eq:mTIR}
mTIR = \frac{\sum_{i = 1}^M L_{p,traffic} - L_{p, interfering}}{M}.
\end{equation}

As it is the sound environment where the traffic is less present, the $mTIR$ is always negative for the \textit{park}. The \textit{interfering} sound class is therefore the main sound source. In the case of the \textit{quiet street}, the $TIR$ can be positive or negative depending on the traffic presence on the scene. For the 2 others sound environments, when the traffic become the main sound source, $mTIR$ is always positive.

To validate its realism, the corpus of transcribed urban sound scenes is submitted to a perceptual test.
